Methodology for Assessing the State of the Practice for Domain X

### 2020-10-29 StateOfPractice/Methodology/Methodology.tex
added comment about performance benchmarks into methodology

\section{Introduction} \label{SecIntroduction}
The scope of this document is to conduct a current state of practice analysis of software in a scientific computing domain for the purpose of understanding quality and assisting in future development. The methodology presented here is part of an overall assessment of the impact of model driven engineering and code generation on the sustainability of scientific computing software. The research proposal for this assessment, which contains a more detailed description of this state of practice exercise, can be found \href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ResearchProposal.pdf}{here}. The research questions that this exercise will answer are found in Section \ref{ResearchQuestions}. Section \ref{StepsAQDS} outlines the steps to be taken.

>>>>

\section{Introduction} \label{SecIntroduction}

\pmi{comment from meeting: remove performance benchmarks from scope of exercise because enough other people consider this. Add similar comment into introduction explaining (link to examples of performance considered elsewhere in similar projects??) why performance is not considered}

The scope of this document is to conduct a current state of practice analysis of software in a scientific computing domain for the purpose of understanding quality and assisting in future development. The methodology presented here is part of an overall assessment of the impact of model driven engineering and code generation on the sustainability of scientific computing software. The research proposal for this assessment, which contains a more detailed description of this state of practice exercise, can be found \href{https://github.com/smiths/AIMSS/blob/master/OverallResearchProposal/ResearchProposal.pdf}{here}. The research questions that this exercise will answer are found in Section \ref{ResearchQuestions}. Section \ref{StepsAQDS} outlines the steps to be taken.
